\textbf{Automated Reasoning\\Practical Assignment -- Part 1}

### 2022-10-10 docs/paper.tex
Add mail
Add program verification explanation

\author{Jelmer Firet (s1023433, \href{mailto:jelmer.firet@ru.nl}{jelmer.firet@ru.nl}) \and
        Bram Pulles()}
\title{\textbf{Automated Reasoning\\Practical Assignment -- Part 1}}

@@

\section{Program safety}

>>>>

\author{Jelmer Firet (s1023433, \href{mailto:jelmer.firet@ru.nl}{jelmer.firet@ru.nl}) \and
Bram Pulles (s1015194, \href{mailto:bram.pulles@ru.nl}{bram.pulles@ru.nl})}
\title{\textbf{Automated Reasoning\\Practical Assignment -- Part 1}}

@@

\section{Program safety}
In order to test whether it is possible for the program to crash we use the SMT
solver to check if the crashing statement can be reached. If the crash cannot
be reached the formula will be unsatisfiable. If the crash can be reached the
formula will be satisfiable and the variable assignment will provide us a value
for the if-statement in every iteration.
\\

We start by creating a variable $l = 10$ for the number of iterations the loop
will make. We also create $l + 1$ integer variables $a_i$ and $b_i$, where
$a_0$ and $b_0$ are the initial values of $a$ and $b$, the others describe the
values of $a$ and $b$ at every iteration of the loop. Lastly, we create $l$
boolean $c_i$ variables to denote the value of the if-statement at iteration
$i$.

\begin{enumerate}
	\item
		We start with adding the constraints for the initial values of $a$ and $b$.
		$$a_0 = 1 \land b_0 = 1$$

	\item
		If the if-statement is true we want to update the values of $a$ and $b$
		accordingly. This is done using the following constraint.
		\[
			\forall_{1 \leq i \leq l + 1}
			\left ( c_{i-1} \to
				a_i = a_{i-1} + 2 \cdot b_{i-1} \land
				b_i = b_{i-1} + i
			\right )
		\]
	\item
		If the if-statement is false we want to update the values of $a$ and $b$
		accordingly. This is done using the following constraint.
		\[
			\forall_{1 \leq i \leq l + 1}
			\left ( \lnot c_{i-1} \to
				b_i = a_{i-1} + b_{i-1} \land
				a_i = a_{i-1} + i
			\right )
		\]
	\item
		At last we want to check whether the program can crash, such that
		$\text{SAT} \leftrightarrow \text{crash}$.
		\[ b_l = 700 + n \]
\end{enumerate}

Running our program with all of these constraints yields the output shown
below. The path shows the consecutive evaluations of the if-statement, with
\texttt{f} as false and \texttt{t} as true, which leads to a crash.

\begin{verbatim}
n = 1 is sat -> crash
path ffttttftff
n = 2 is unsat
n = 3 is unsat
n = 4 is sat -> crash
path ttfftftttf
n = 5 is unsat
n = 6 is sat -> crash
path tftfffttff
n = 7 is unsat
n = 8 is sat -> crash
path ttftftftft
n = 9 is unsat
n = 10 is sat -> crash
path ttfttftttf
\end{verbatim}
